Correlating Scanning Ion Conductance and Super-Resolved Fluorescence Microscopy

### 2020-10-19 sections/pitfalls.tex
reworked

% Instead of having to worsen SICM resolution to match FM resolution, it might be 
% reasonable to combine SICM and SRFM in one setup. Though, this implementation
% comes with its own potential pitfalls, especially as due to the super resolution
% of both techniques small deviations or disturbances are sufficient to ruin the 
% alignment of the setup. Some of these potential pitfalls are discussed in the 
% following:

% To avoid some problems from the beginning, both the SRFM and SICM setups
% should provide spatial resolutions in the same range. Also, if possible, one
% software should be used to control both setups to prevent delays in the
% imaging process due to transmitting information from one software to the other.

@@

Especially the second option would require repeated
focal plane adjustment of the optical setup. In turn, this requires meticulous
alignment of the excitation and depletion beam to retain the super-imposition
of the two beams during the adjustment of the focal plane. To minimize the
pixels that require an adjustment of the focal plane, the adjustment has been
only applied if a $z$-range of more than one micrometer was exceeded
\cite{Novak2014}. If STED recordings with increased vertical resolution are
intended, the acceptable range for not adjusting the focal plane decreases,
which in turn might lead to longer and less stable recordings.

Due to the increased horizontal resolution, even the $x,y$-alignment of SICM
pipette and the laser beams becomes more challenging since the tolerable
offset between the two decreases. While it has been reported that fine
adjustment screws are sufficient to align the pipette and the beam in the
combination of SICM and confocal microscopes \cite{Gorelik2002a,
  Shevchuk2008,Novak2014}, additional piezo elements might be required for the
alignment of STED and SICM.

>>>>

@@

Especially the second option would require repeated
focal plane adjustment of the optical setup. If this is implemented by moving
the objective (Fig.~\ref{fig:sscm_setup}b), this requires meticulous
alignment of the excitation and depletion beam to retain the super-imposition
of the two beams during the adjustment of the focal plane.

To minimize the
pixels that require an adjustment of the focal plane, the adjustment has been
only applied if a $z$-range of more than one micrometer was exceeded
\cite{Novak2014}. However, the resolution of STED microscopy depends on
the intensity of the depletion beam, which decreases along the optical
axis. Thus, the range for unadjusted imaging might decrease and, if STED
recordings with increased vertical resolution are
targeted, will decrease even further,
which in turn might lead to longer and less stable recordings.

Due to the increased horizontal resolution, even the $x,y$-alignment of SICM
pipette and the laser beams becomes more challenging since the tolerable
offset between the two decreases. While it has been reported that fine
adjustment screws are sufficient to align the pipette and the beam in the
combination of SICM and confocal microscopes \cite{Gorelik2002a,
  Shevchuk2008,Novak2014}, additional piezo actors might be required for the
alignment of STED and SICM. However, for the alignment of the SICM pipette and a
confocal beam by piezo actors a remaining offset in the alignement has been
reported \cite{Bednarska2020}.
